---
title: "AccelData_Processing"
author: "Chris Moore"
date: "December 6, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Required packages
```{r}
library(tidyverse)
library(RSQLite)
library(PhysicalActivity)
load_all("./Accelerometer")
```

# Step 1: Prepare data

## 1a) Take 1-sec epoch data exproted by accelerometer software and add a time stamp, reintegrate to 60-sec, add a day variable, and classify wear time to create 'PrepedData' files
```{r}
?acceldata_prep
acceldata_prep(input_dir = "./Data", file_pattern = "*1secAGdata.csv", 
               output_dir = "./Outputs", subjectID_length = 2,
               subjectID_start = 1)
```
Also created custom function for reintegrating 1-sec epoch files to 60-sec epoch ('reintegrate_accel' function in R folder, just to try, function not complete with documentation)

## 1b) Import 'PrepedData' files, use sleep logs to filter out data collected during sleep, and create 'FilteredWakeData' files
```{r}
?sleep_filter
sleep_filter(acceldata_dir = "./Outputs", sleeplog_dir = "./Data",
             output_dir = "./Outputs", subjectID_length = 2, 
             accelfile_pattern = "^PrepedData", sleeplog_pattern = "*SleepLog",
             accelfile_IDstart = 12, sleeplog_IDstart = 1)
```


# Step 2: Examine physical activity with counts

## Import prepped and filtered data from Step 1
```{r}
import_data <- read.csv("./Outputs/FilteredWakeData_CM.csv")
```

## 2) Classify physical activity intensity and summarize MVPA and sedentary time per day, per week and for weekday vs weekend
```{r}
?pai_week_summary
pai_week_summary(import_data)

pai_byday
pai_weekavg
pai_byweekday_end
```


# Step 3: Examine physical activity with steps

## 3) Summarize total steps for each day, average steps/day over the week, and average steps/day on weekdays vs weekends
```{r}
?steps_week_summary
steps_week_summary(import_data)

steps_byday
steps_weekavg
steps_byweekday_end
```


# Step 4:Data visualization

## 4a) Plot counts vs time using 'PhysicalActivity' package
```{r}
?plotData
plotData(import_data, cts = "axis1", TS = "TimeStamp")
```

## 4b) Plot steps vs time
```{r}
?plot_steps
plot_steps(import_data)
```

## 4c) Plot comparison of weekday versus weekend physical activity 
```{r}
?plot_weekday_vs_end # REP mvpa_plot
plot_weekday_vs_end(pai_byweekday_end, steps_byweekday_end, "CM")

plot_pai_dayend
plot_steps_dayend
```